### 2017-03-23 Manuscripts/cog-psych/cogpsych.tex
xor-cluster-row sample plot works

@@

On average, the axis ranges of generated categories tends to reflect those of the experimenter-defined categories. However, this cannot be said for the correlation between features in the generated categories.

% ----  yrange: Cluster, Row
% T = 4.5714, p = 1.16282e-05 Means: 0.9023 (0.7495), 0.3566 (0.5553),

% ----  yrange: Cluster, XOR
% T = -3.952, p = 0.0001313583    Means: 0.9023 (0.7495), 1.4224 (0.6858),

% ----  yrange: Row, XOR
% T = -9.2603, p = 0.0    Means: 0.3566 (0.5553), 1.4224 (0.6858),

% ---- Row X vs. Y:
% T = 11.1735, p = 0.0    Means: 1.5738 (0.5678), 0.3566 (0.5553),

% ---- Cluster X vs. Y:
% T = -0.1258, p = 0.9002773681   Means: 0.8828 (0.7768), 0.9023 (0.7495),

% ---- XOR X vs. Y:
% T = -1.331, p = 0.1885039643    Means: 1.2586 (0.7542), 1.4224 (0.6858),

@@

% ---- XOR has more total range than Cluster?
% T = -4.8918, p = 3.1371e-06 Means: 1.7852 (0.9012), 2.681 (1.1023),

% ---- XOR has more total range than Row?
% T = -4.3418, p = 3.0207e-05 Means: 1.9303 (0.7412), 2.681 (1.1023),

% ----  yrange: Cluster, Row
% T = 4.5714, p = 1.16282e-05 Means: 0.9023 (0.7495), 0.3566 (0.5553),

% ----  yrange: Cluster, XOR
% T = -3.952, p = 0.0001313583    Means: 0.9023 (0.7495), 1.4224 (0.6858),

% ----  yrange: Row, XOR
% T = -9.2603, p = 0.0    Means: 0.3566 (0.5553), 1.4224 (0.6858),

>>>>

It is firstly worth noting that we observed a substantial degree of individual differences in our data. In Figure \ref{fig:e1-samples} we have plotted sample data from several participants, from which it evident that different participants assumed qualitatively distinct approaches to category generation. In this section we will focus on what can be learned from analyzing the data in aggregate, but in later sections we will explore how individual differences can be explained.

@@

On average, the axis ranges of generated categories tends to reflect those of the experimenter-defined categories. However, this cannot be said for the correlation between features in the generated categories. As in the experimenter-defined categories,

@@
